\href{https://www.youtube.com/watch?v=hf1DkBQRQj4}{Omedetou}, you made it all the way to the end of this long guide. I will use this
section to deliver some of my thoughts going into developing this guide, state of Fallout 4 modding scene and the people who helped 
or justed wanted to say hi.\\
I \textit{officially} started with this guide on August 1st but had already thought about most things two weeks before that. I took 
an \textit{apprentice} on July 20th who actually tried converting from a CBBE Mesh to Fusion Girl BodySlide. The only kind real 
guide you had was those 10 steps on the CBBEToFusionGirl reference mod page but that one had no depth. As I got more questions 
from multiple people that all make the same mistakes or miss the same details, I decided it was time to finally start with this guide.\\
The watchful eye will probably know that this guide was written using LaTeX (or you just looked at the source code :p). I used LaTeX
because I hate Microsoft, Open and Libre Office and used it before to write my thesis and multiple presentations. I simply could not 
resist writing my guide in LaTeX using Visual Studio Code as a programmer. I still haven't figured out the reason why some of the 
pictures are positioned so weird and why \textit{wrapfigure} sometimes is forced to float. Anyway, I didn't know how many pages I would 
need for this guide and I hope it wasn't too much. The last guide I made was for Ultimate Skyrim to change all ugly NPCs and the PC 
to decent looking human beings. The scale of that guide isn't on par with this one because I had more to explain than simple modding 
procedures.\\
I actually would not have thought that I would end up doing BodySlide Conversions but here I am, having converted more than 30 
outfits to the Fusion Girl body. The truth is that I returned to Fallout 4, after a long period of intensive Oblivion, Skyrim and 
Skyrim Special Edition modding, to start a new modded play through with \href{https://www.nexusmods.com/fallout4/mods/28085}{Project Valkyrie} 
as the main mod. I did a clean installation of the game and after getting every mod I wanted for the time being, I looked for some 
character presets because I am total shit at doing them. It was than that I found the \href{https://www.nexusmods.com/fallout4/mods/39081}{Diana 2.0 LooksMenu Preset} 
by my good friend \href{https://www.nexusmods.com/fallout4/users/8744746}{dreamchaser1983}. And that character also came with 
its own \href{https://www.nexusmods.com/fallout4/mods/39010}{BodySlide preset} but not for CBBE but for Fusion Girl. I quickly took 
interest in the Fusion Girl body and started looking into available conversions of the outfits I already downloaded. There were a few, 
most of them had clipping due to the huge ass of the preset. I had vacation so I thought I would just convert them as I already had 
some experience converting from CBBE to AB. Well, this is how I met your mother.\\
Like I said above, I actually wanted to play Fallout 4 again. I never really liked the modding scene of Fallout 4 that much. I prefer 
Skyrim because of the opportunities it has and the fact that I love magic related stories. Fallout 4 also wasn't really a good game.
Compared to Fallout New Vegas or Fallout 3, Fallout 4 was more mainstream oriented with more guns than stories. The game was not a 
good base for modding which reflected in the amount of mods in each categories. You got a lot of weapons, outfits and of course retextures 
but again, same as the base game, not enough quest mods. In Skyrim you have good stuff like Vigilant, Moonpath to Elsweyr, Moon and Star,
The Forgotten City, fucking Armorous Adventures and sure, Fallout 4 does have mods like Project Valkyrie I talked about or Fusion City 
Rising, Outcasts and Remnants or the game-jam like 50 Ways to Die at Dr. Nick's but the base game doesn't give much opportunities for 
story telling.\\
Now, I know that this little rant of mine is very biased and it shows how I felt \textbf{before} doing conversions. After I started, I 
had to get involved in the modding scene of Fallout 4 and made new friends, found new amazing authors and actually started to enjoy 
Fallout 4. In programming you have a multitude of languages to choose from. "You program to the strength and weaknesses of the language".
I believe that this can be applied to modding.\\
"You mod to the strength and weaknesses of the game" - erri120\\
Yeah, I like that. Anyway, being involved and being an author instead of an user changed my perspective on the game. I don't know how 
long I will continue doing conversions or how many I will do, which is the reason I hope you learned something from this guide and 
decide to start converting outfits yourself.\\
\textbf{Thanks}\\
Thanks to dreamchaser1983 for making me interested in Fusion Girl, helping me getting started and taking some amazing screenshots.\\
Thanks to the whole Fusion Girl team for creating this amazing body and helping me on the Discord.\\
Thanks to all mod authors of outfits I converted. I loved all of the outfits.\\
Thanks to Souichirou for being my apprentice.\\